HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex

\begin{table}[t]
\begin{center}
\begin{tabular}{l|cccc}
& cs & de & pl & ro \\
\hline
Annot. 1 & 255 & 140  & 138 & 96 \\
Annot. 2 & -- & 162 & 229 & 207 \\
\end{tabular}
\caption{Median annotation times per sentence, in seconds.
We do not give times for the second Czech 
``annotator'', since this was a collection of annotators, working in parallel.}
\label{tab:annot_times}
\end{center}
\end{table}

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

@@

HMEANT shares much of HUME's motivation in defining a
measure that decomposes over semantic units, rather than strings. On the other
hand, there are important differences in design decisions, which we summarize in this
section.

@@

\paragraph{Cost of Structural Annotation}

HMEANT structural annotation (semantic role labelling, SRL), similar to e.g.
PropBank
\parcite{palmer2010semantic}, is designed to be very simple and easy to explain
to lay annotators.
HUME relies on UCCA, which is arguably more abstract, harder to
explain, and thus more expensive to obtain.

On the other hand, HUME 
needs the semantic annotation
done once for a given source sentence, whereas for the HMEANT set-up, every new
MT output has to be structurally annotated.\oa{we can give some empirical data here.
  In the WMT 13 experiment, Lexi and Barry report a little over 3 mins of annotation
  per sentence + 3 translations. HUME annotation is about 2-4 minutes per sentence.
  UCCA annotation by trained annotators is about 700 tokens/hour (we didn't
  check it for individual sentences), but that's done only once so it should be amortized.}

>>>>

\begin{table}[t]
\begin{center}
{\small
\begin{tabular}{l|cccc}
& cs & de & pl & ro \\
\hline
Annot. 1 & 255 & 140  & 138 & 96 \\
Annot. 2 & -- & 162 & 229 & 207 \\
\end{tabular}
\caption{Median annotation times per sentence, in seconds.
We do not give times for the second Czech 
``annotator'', since this was a collection of annotators, working in parallel.}
\label{tab:annot_times}
}
\end{center}
\end{table}

@@

\begin{table}[t]
\begin{center}
{\small
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
}
\end{center}
\end{table}

@@

Like HMEANT, HUME defines  a
measure that decomposes over semantic units, rather than strings. 
However, there are important differences in design decisions, which we summarize in this
section.

@@

%
%\paragraph{Cost of Structural Annotation}
%
%HMEANT structural annotation (semantic role labelling, SRL), similar to e.g.
%PropBank
%\parcite{palmer2010semantic}, is designed to be very simple and easy to explain
%to lay annotators.
%HUME relies on UCCA, which is arguably more abstract, harder to
%explain, and thus more expensive to obtain.
%
%On the other hand, HUME 
%needs the semantic annotation
%done once for a given source sentence, whereas for the HMEANT set-up, every new
%MT output has to be structurally annotated.\oa{we can give some empirical data here.
%  In the WMT 13 experiment, Lexi and Barry report a little over 3 mins of annotation
%  per sentence + 3 translations. HUME annotation is about 2-4 minutes per sentence.
%  UCCA annotation by trained annotators is about 700 tokens/hour (we didn't
%  check it for individual sentences), but that's done only once so it should be amortized.}
